\vspace{-1cm}\normalsize{\textbf{Fairly Random: Impact of Winning the Toss on the Probability of Winning}}

### 2015-09-19 write_up/cricket.tex
better results intro

\section*{Results}
A caveat about interpretation before we discuss the results. As we allude to at the start, it is hard, if not impossible, to distinguish between lack of advantage of winning a toss and not capitalizing on the potential advantage.

>>>>

\section*{Results}
A caveat about interpretation before we report the results. As we discuss in the introduction, we cannot estimate the actual advantage of winning a toss. We can only estimate the net observed advantage, which is the extent to which the teams capitalize on the potential advantage.
